Nabi - A Preventative Solution Against JavaScript and Scriptless Tabnabbing Attacks

### 2015-04-28 paper/paper.tex
Finished TabSol section

The process of TabShots begins with a simple whitelisting check, to check whether the newly opening URL has already been verified as legitimate.  If so, the process execution is stopped.  Otherwise, TabSol will calculate the hash digest of the web page source to save the current state of the page, using the cryptographic hash function SHA-1.  When the user switches back to the old tab, TabSol will recompute the hash digest of the page, and compare it to the stored digest.  If they match, TabSol determines that the site is legitimate and adds the page into the domain whitelist mentioned above.  Else, the page is treated as suspicious, and TabSol attempts to find a login form on the changed page, as the authors consider its presence necessary in a phishing attack.  The authors chose to sue the login form detction method presented in CANTINA+.  If a login form is present, then the page is considered a phishing webpsge attempting tabnabbing, and appropriate actions can be taken.

@@

>>>>

The process of TabShots begins with a simple whitelisting check, to check whether the newly opening URL has already been verified as legitimate.  If so, the process execution is stopped.  Otherwise, TabSol will calculate the hash digest of the web page source to save the current state of the page, using the cryptographic hash function SHA-1.  When the user switches back to the old tab, TabSol will recompute the hash digest of the page, and compare it to the stored digest.  If they match, TabSol determines that the site is legitimate and adds the page into the domain whitelist mentioned above.  Else, the page is treated as suspicious, and TabSol attempts to find a login form on the changed page, as the authors consider its presence necessary in a phishing attack.  The authors chose to sue the login form detction method presented in CANTINA+.  If a login form is present, then the page is considered a phishing web page attempting tabnabbing, and appropriate actions can be taken.

@@

The authors do leave some issues of TabSol unaddressed in their paper.  First, the authors make the fundamental assumption that any tabnabbing page will have a login form.  This can be simply avoided by using a tabnabbing page that uses alternative means of communication such as a phone number, email address, or even a link to another login page.  The login form detection system will completely fail in detecting these types of phishing attacks.  Second, TabSol immediately and prematurely place any site that has matching hashes onto the whitelist, which could result in malicious sites being placed onto the whitelist.  If the user switches away and back to the tab before the malicious tab is scheduled to change, the tab will not change at all, and it will pass TabSol testing and be placed on the blacklist.  This login form basis and premature whitelisting can easily lead to the infiltration of tabnabbing sites.
